Towards human SuperEEG

### 2018-10-07 paper/main.tex
backing up progress-- almost done with first pass through results; working on fig 5 caption [WIP]

To gain insights into whether particular electrode locations might be
especially informative, we first computed the average reconstruction
accuracy across all of each patient's electrodes (using the
across-patients cross validation test; black histograms in
Fig.~\ref{fig:corrmap}A and C).  We labeled each patient's electrodes
in each dataset with the average reconstruction accuracy for that
patient.  In other words, we assigned every electrode from each
patient the same value, reflecting how well the activity patterns at
those electrodes were reconstructed on average.  Next, for each voxel
in the 4~mm$^3$ MNI brain, we computed the average value across any
electrode (from any patient) that came within 20 MNI units of that
voxel's center.  Effectively, we computed the average reconstruction
accuracy across any patients with electrodes near each voxel, where
the avearges were weighted to reflect patients who had more electrodes
implanted near that location.

\textbf{JRM STOPPED HERE}
% - report most-informative locations (i.e. which brain structures?)
% - can we say anything bout whether these most-informative regions are heavily
% interconnected, e.g. perhaps from the resting state literature?

To gain insights into this question, we
computed the average reconstruction accuracy for each patient, then
computed the average patient reconstruction correlation for any
patients who had electrodes within a 20 MNI unit diameter sphere
centered on each voxel location. The resulting maps highlight the
locations of implanted electrodes from patients whose reconstructions
were especially accurate (Fig.~\ref{fig:informap}A and B). We found
that the most informative locations were consistent across datasets
which lends support to the notion that different electrode location
are more informative about activity across patients
(Fig.~\ref{fig:informap}C); $r = 0.22, p < 10^{-10}$).  The locations
in dark red might therefore be good candidate implantation targets for
neurosurgeons and neurologists who wish to use SuperEEG to reconstruct
full-brain electrophysiological signals.  The above findings, that one
can infer brain activity throughout a person's brain using recordings
from a limited number of locations from that person's brain in
conjunction with recordings from other people's brains, have deep
implications for the structure of brain data.  The first implication
is that the correlational structure of different people's brain data
is largely preserved across individuals. Despite recent evidence that
different people have stable but reliably different resting state
connectome~\cite{FinnEtal15}, our results suggest that the
correlational structure of different people's brain data is preserved
enough across individuals to provide meaningful information.

>>>>

To gain insights into whether particular electrode locations might be
especially informative, we first computed the average reconstruction
accuracy across all of each patient's electrodes (using the
across-patients cross validation test; black histograms in
Fig.~\ref{fig:corrmap}A and C).  We labeled each patient's electrodes
in each dataset with the average reconstruction accuracy for that
patient.  In other words, we assigned every electrode from each
patient the same value, reflecting how well the activity patterns at
those electrodes were reconstructed on average.  Next, for each voxel
in the 4~mm$^3$ MNI brain, we computed the average value across any
electrode (from any patient) that came within 20 MNI units of that
voxel's center.  Effectively, we computed an \textit{information
  score} for each voxel, reflecting the average reconstruction
accuracy across any patients with electrodes near each voxel-- where
the averages were weighted to reflect patients who had more electrodes
implanted near that location. This yielded a single map for each
dataset, highlighting regions that are especially promising
implantation targets in terms of providing full-brain activity
information via SuperEEG (Fig.~\ref{fig:informap}A, B).  Despite task
and patient differences across the two datasets, we nonetheless found
that the maps of the most promising implantation targets derived from
both datasets were similar (voxelwise correlation between information
scores across the two datasets: $r = XXX, p = XXX$).  While the
correspondence between the two maps was not perfect, our finding that there were
some commonalities between the two maps lends support to the notion
that different brain areas are differently informative about
full-brain activity patterns.  Further, regions like XXX and XXX that
exhibited strong information scores in both datasets may be especially
promising implantation targets.

\textbf{JRM STOPPED HERE}
